A latency-tolerant runtime for large graph computations

### 2011-01-13 doc/hotpar2011/softxmt-hotpar2011.tex
intro and conclusion
minor comment  in intro

\title{Latency-tolerant runtime for large graph computations}

@@

And these graphs can be large---too large for a single node. In
January 2011, Facebook had 500 million active users with an average of
130 friends each \cite{Facebook:2011p91}. A natural approach would be
to try to partition the graph across the nodes in a cluster. But with
low diameter graphs, a traversal starting at any node is likely to
quickly leave its partition and travel over the network, incurring
high latency costs. And power law graphs have a small number of nodes
that generate significantly more work that other nodes, leading to
computational imbalance.

>>>>

\title{A latency-tolerant runtime for large graph computations}

@@

And these graphs can be large---too large for a single node \todo{may want to avoid saying 'node' since graph 'node' is also used in this paragraph}. In January 2011, Facebook had 500 million active users with an average of
130 friends each \cite{Facebook:2011p91}. A natural approach would be
to try to partition the graph across the nodes in a cluster. But with
low diameter graphs, a traversal starting at any node is likely to
quickly leave its partition and travel over the network, incurring
high latency costs. And power law graphs have a small number of nodes
that generate significantly more work than other nodes, leading to
computational imbalance.
